### 2012-06-23 inst/examples/value_of_information.Rmd

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information_symmc/", verbose=TRUE or`

@@

  z_g <- function() rnorm(1,  0, policy_g) 
  z_m <- function() rnorm(1,  0, policy_m) 
  z_i <- function() rnorm(1,  0, policy_i)

@@

``` {r runall}
lvl <- 0.1
det <- scenario(0, 0.0, 0.0)
g <- scenario(lvl, 0.0, 0.0)
m <- scenario(0.0, lvl, 0.0)
i <- scenario(0.0, 0.0, lvl)
gm <- scenario(lvl, lvl, 0.0)
gi <- scenario(lvl, 0.0, lvl)
gmi <- scenario(lvl, lvl, lvl)
````

@@

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rnorm(1,  0, true_g)
  z_m <- function() rnorm(1,  0, true_m) 
  z_i <- function() rnorm(1,  0, true_i)

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`

@@

  z_g <- function() rlnorm(1,  0, policy_g) 
  z_m <- function() rlnorm(1,  0, policy_m) 
  z_i <- function() rlnorm(1,  0, policy_i)

@@

``` {r runall}
lvl <- 0.2
det <- scenario(0, 0.0, 0.0)
g <- scenario(lvl, 0.0, 0.0)
m <- scenario(0.0, lvl, 0.0)
i <- scenario(0.0, 0.0, lvl)
gm <- scenario(lvl, lvl, 0.0)
gi <- scenario(lvl, 0.0, lvl)
gmi <- scenario(lvl, lvl, lvl)
````

@@

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rlnorm(1,  0, true_g)
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)
